Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-07 draft.tex
add defn of stationary markov eqm to draft

We provide a set of conditions under which perpetual unrecognized statehood is the outcome of a subgame-perfect equilibrium of this game. %This requires that the patron is both willing and able to make investments sufficient to (a) offset the deterioration in the secessionists' status quo payoffs and (b) deter the international community from making investments that would induce a negotiated settlement. That is, it must be that the prospect of reunification is more important for the patron to avoid than for the international community to achieve. Additionally, in order for the status quo to persist, preferences must be such that recognition of the secessionist state is more important for the international community to avoid than for the patron to achieve; otherwise, the international community will not be able to deter the patron from making investments to instigate recognition.
Somewhat counterintuitively, in this equilibrium a patron will expend resources every period if necessary to sustain the status quo of unrecognized statehood even when the patron would prefer that the secessionists achieve recognized independence. This occurs when the international community's preferences against recognition are sufficiently strong---as is almost always likely to the case---to make it prohibitively expensive for the patron to facilitate recognition in the face of counteractivity by the international community.

@@

@@

There are many other potential equilibrium outcomes of this game, including, under the right parameters, immediate ceding by either party as well as fighting (see Section~\ref{sec:alt}). As we are interested particularly in the outcome of long-term unrecognized statehood, here we focus on the question of the existence of an equilibrium that leads to this outcome in perpetuity. We will use the solution concept of subgame perfect equilibrium to show that, given the sufficient conditions in Proposition 1, at least one status quo equilibrium will exist.\\

@@

>>>>

We provide a set of conditions under which perpetual unrecognized statehood is the outcome of a stationary Markov equilibrium of this game. %This requires that the patron is both willing and able to make investments sufficient to (a) offset the deterioration in the secessionists' status quo payoffs and (b) deter the international community from making investments that would induce a negotiated settlement. That is, it must be that the prospect of reunification is more important for the patron to avoid than for the international community to achieve. Additionally, in order for the status quo to persist, preferences must be such that recognition of the secessionist state is more important for the international community to avoid than for the patron to achieve; otherwise, the international community will not be able to deter the patron from making investments to instigate recognition.
Somewhat counterintuitively, in this equilibrium a patron will expend resources every period if necessary to sustain the status quo of unrecognized statehood even when the patron would prefer that the secessionists achieve recognized independence. This occurs when the international community's preferences against recognition are sufficiently strong---as is almost always likely to the case---to make it prohibitively expensive for the patron to facilitate recognition in the face of counteractivity by the international community.

@@

Our concept of equilibrium will be stationary Markov equilibrium as defined in Mailath and Samuelson (2006). That is, a strategy profile is a stationary Markov equilibrium if it is a stationary Markov strategy profile and a subgame-perfect equilibrium. In turn, a strategy profile is defined to be a stationary Markov strategy if any two ex post histories terminating in the same state play identically from the termination point forward. That is, stationary Markov strategies ignore all details of the history aside from the current state.

@@

\textbf{There are many other potential equilibrium outcomes of this game, including, under the right parameters, immediate ceding by either party as well as fighting (see Section~\ref{sec:alt}). As we are interested particularly in the outcome of long-term unrecognized statehood, here we focus on the question of the existence of an equilibrium that leads to this outcome in perpetuity. We will use the solution concept of stationary Markov equilibrium to show that, given the sufficient conditions in Proposition 1, at least one status quo equilibrium will exist.}\\

@@

\item \hangindent=1cm Mailath, George J., and Larry Samuelson. 2006. "Repeated Games and Reputation." New York, NY: Oxford University Press.
